---
title: "About us"
description: |
  Who we are and what we do
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
```


## The gist 

We are a team based at the [London School of Hygiene & Tropical Medicine](https://www.lshtm.ac.uk) who focus on real-time modelling and forecasting of infectious disease outbreaks. We are funded by the Wellcome Trust and work in collaboration with a number of other research groups, public health agencies and non-governmental organisations. Our main aim is to develop and use modelling methodology that makes the most of available resources to provide insights useful for outbreak response, control and prevention. 

```{r}
team <- fs::dir_ls("_data/team") %>%
  purrr::map(yaml::read_yaml)

# Put Seb first (group leader)
team <- c(
  team[which(purrr::map(team, "name") == "Sebastian Funk")],
  team[-which(purrr::map(team, "name") == "Sebastian Funk")]
)
```

## The team

```{r}
current_team <- team %>%
  purrr::keep(function(x) x[["current-member"]])
```

```{r, results='asis'}
current_team %>%
  purrr::map_chr(function(e) {
    knitr::knit_expand(
      "_team_member.Rmd", 
      name = e[["name"]],
      webpage = e[["webpage"]],
      github = e[["github"]],
      twitter = e[["twitter"]],
      orcid = e[["orcid"]],
      description = e[["description"]]
    )
  }) %>%
  { knitr::knit_child(text = unlist(.), quiet = TRUE) } %>%
  cat(sep = "\n")
```

## Former team members

[Flavio Finger](https://ffinger.github.io/) · [Joe Palmer](https://pure.royalholloway.ac.uk/portal/en/persons/joseph-palmer(dce02baf-426d-4ea1-a242-818b7cf5158a).html) · [Robin Thompson](https://warwick.ac.uk/fac/sci/maths/people/staff/thompson/) · Joel Hellewell
