---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/",
  echo = FALSE
)
library(magrittr)
```

## How to create or edit a team member ID card

This folder contains all the (current and former) team member ID cards. 

When a new person join the team, they should create a new ID card. When a person
leaves the team, they should switch the `current-member` flag to `false` (but
not delete their card as it is used to list the former team members).

```{r}
schema <- yaml::read_yaml("_schema.yml")
```

The validity of the yaml file is automatically checked with a [GitHub Action](https://github.com/epiforecasts/epiforecasts-distill/blob/main/.github/workflows/validate-team-member-id.yaml)
on pushes and pull requests.

### Mandatory fields

```{r, results='asis'}
schema %>% 
  purrr::pluck("properties") %>%
  purrr::keep(names(.) %in% schema$required) %>%
  purrr::imap(~ c("value" = .y, .x)) %>%
  purrr::map(~ knitr::knit_expand(text = "#### `{{.x$value}}`\n `{{.x$type}}`\n\n{{.x$description}}\n")) %>%
  { knitr::knit_child(text = unlist(.), quiet = TRUE) } %>%
  cat(sep = "\n")
```

### Optional fields

```{r, results='asis'}
schema %>% 
  purrr::pluck("properties") %>%
  purrr::keep(!names(.) %in% schema$required) %>%
  purrr::imap(~ c("value" = .y, .x)) %>%
  purrr::map(~ knitr::knit_expand(text = "#### `{{.x$value}}`\n `{{.x$type}}`\n\n{{.x$description}}\n")) %>%
  { knitr::knit_child(text = unlist(.), quiet = TRUE) } %>%
  cat(sep = "\n")
```

